%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.

%
% Creator Peilin Li
% Contact me via twitter/wechat: @pe1l1nl1
% linkedin.com/peill and/or github/ppeill
% Inspired by Peppa Pig 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.40in,top=0.4in,right=0.75in,bottom=0.4in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{times}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
% \begin{center}

% \end{center}
\name{Jihoon Lee} % Your name 


%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\faEnvelope{leejihoon@snu.ac.kr}}
\address{\faPhone(+82)10-2447-5082} % Your address

\begin{document}
%{\centerline {\em \textbf { Ph.D. Candidate at Seoul National University } } }
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Education}
%
%{\bf Seoul National University, Seoul, Republic of Korea } \hfill {\em Sep 2014 - Present} 
%\\{ \textit {Ph.D. in Aerospace Engineering}} 
%\\{ \textit {Flight Dynamics and Control Lab}} 
%\\{ \textit {Supervisor: Youdan Kim}} 
%
%{\bf Yonsei National University, Seoul, Republic of Korea } \hfill {\em Mar 2013 - Aug 2014} 
%\\{ \textit {B.S. in Astronomy (Double Major)}}
%
%{\bf Yonsei National University, Seoul, Republic of Korea } \hfill {\em Mar 2010 - Aug 2014} 
%\\{ \textit {B.S. in Mechanical Engineering}} 
%\\{ \textit {Thesis: Modeling and PIDE Control Simulation of a Quadrotor}} 
%\\{ \textit {Supervisor: Jongsoo Lee}} 
%
%{\bf Sangam High School, Seoul, Republic of Korea } \hfill {\em Mar 2007 - Feb 2010} \\
%
%{\bf Youngnam Middle School, Seoul, Republic of Korea } \hfill {\em Mar 2004 - Feb 2007}\\ 
%
%{\bf Seoul Shinyoung Elementary School, Seoul, Republic of Korea } \hfill {\em Mar 1998 - Feb 2004} 
%
%\end{rSection}

%\begin{rSection}{Skills}
%
%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Discipline: \ & 
%Aerospace Engineering, Electrical Engineering, Aeronautical Engineering, 
%\\ & Mechanical Engineering, Astronomy, Astrophysics, Physics, 
%\\ & Mechatronics, Systems Engineering, Industrial Engineering, Control Engineering, 
%\\ & Mechanics, Materials Engineering, Fluid Dynamics, Astrodynamics, 
%\\ & Artificial Intelligence, Aviation, Robotics, Signal Processing, 
%\\ & Flight Engineering, Orbital Mechanics, Machine Learning \\	
%
%Expertise: \ & 
%Linear Control, , Nonlinear Control, Robust Control, Adaptive Control, \\ &
%Modeling, Simulation, Algorithm, Optimization, Path Planning, Motion Planning, Filtering \\	
%
%Languages: \ & Korean (Native), English (Professional) \\
%
%Programming: \ & MATLAB, C, C++, Python, LaTeX \\
%
%Software: \ & MATLAB, Simulink, GMAT, SolidWorks, Fluent, LabVIEW, XFLR5, X-Plane, STK \\
%\end{tabular}
%
%\end{rSection}

% \begin{rSection}{Carrier Objective}
%  To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
% \end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
%\begin{rSection}{Research Experience}
%
%{\bf Flight Dynamics and Control Lab, Seoul National University, Seoul, Republic of Korea} \hfill {\em Aug 2014 - Present} 
%\\{\textit{ Student Researcher }}

%{\bf Work Station x,Strange Place x} \hfill {\em June 20xx - April 20xx} 
%\\{\textit{ Engineer}}
%\\- xxx
%\\- xxx

%\end{rSection}

\begin{rSection}{Publication}
	\textbf{JOURNAL}
	\begin{enumerate}\renewcommand{\labelenumi}{[J.\theenumi]}
		\item \textbf{Jihoon Lee}, Heein Park, Youdan Kim, Chan Gook Park, and Jae Hong Lee, "Multi-level Indoor Path Planning and Clearance-based Path Optimization for Search and Rescue Operations," \textit{TBD}, In Preparation.
		
		\item \textbf{Jihoon Lee}, Suwon Lee, Youngjun Lee, Youdan Kim, Yongjun Heo, and Taedong Yoon, "Performance Veriﬁcation of a Target Tracking System with a Laser Rangeﬁnder," \textit{IEEE Access}, Vol. 9, 2021. 30993-31009. \newline[DOI: 10.1109/ACCESS.2021.3060061] 
		
		\item \textbf{Jihoon Lee} and Youdan Kim, "Neural Network-Based Nonlinear Dynamic Inversion Control of Variable-Span Morphing Aircraft," \textit{Proceedings of the Institution of Mechanical Engineers, Part G: Journal of Aerospace Engineering}, Vol. 234, No. 10, 2020, pp. 1624-1637. \newline[DOI: 10.1177/0954410019846713]
		
		\item Seokwon Lee, \textbf{Jihoon Lee}, Somang Lee, Hyunjin Choi, Youdan Kim, Seungkeun Kim, and Jinyoung Suk, "Sliding Mode Guidance and Control for UAV Carrier Landing," \textit{IEEE Transactions on Aerospace and Electronic Systems}, Vol. 55, No. 2, 2019, pp. 951-966. \newline[DOI: 10.1109/TAES.2018.2867259]
	\end{enumerate}\renewcommand{\labelenumi}{\theenumi.}
	
	\textbf{CONFERENCE}
	\begin{enumerate}\renewcommand{\labelenumi}{[C.\theenumi]}
		
		\item Sangmin Lee, Hyeonggwan Kang, \textbf{Jihoon Lee}, and Youdan Kim, "Optimal Policy of Pitch-Hold Phase for Mine Detection of UAV based on Mixed-Integer Linear Programming," \textit{13th Asia-Pacific International Symposium on Aerospace Technology (APISAT 2021)}, Jeju, Korea, Nov. 2021. 
		
		\item Hyeonggwan Kang, Sangmin Lee, \textbf{Jihoon Lee}, Youdan Kim, Jinyoung Suk, and Seungkeun Kim, "Altitude Tracking of UAV with Pitch-Hold Constraint Based on Model Predictive Control for Mine Detection," \textit{21st International Conference on Control, Automation and Systems (ICCAS 2021)}, Jeju, Korea, Oct. 2021. \newline[DOI: 10.23919/ICCAS52745.2021.9649884]
		
		\item \textbf{Jihoon Lee}, Seong-hun Kim, Seungyun Jung, Hanna Lee, and Youdan Kim, "Aircraft Autopilot Design Using Asymmetric Variable-Span Wing Morphing," \textit{32nd Congress of the International Council of the Aeronautical Sciences (ICAS 2021)}, Shanghai, China, Sep. 2021. 
		
		\item Seungyun Jung, \textbf{Jihoon Lee}, Seong-hun Kim, Hanna Lee, and Youdan Kim, "Disturbance Observer-Based Pitch Autopilot for Morphing UAV during Transition Phase," \textit{2020 AIAA Science and Technology Forum and Exposition (SciTech 2020)}, Orlando, FL, Jan. 2020. \newline[DOI: 10.2514/6.2020-1087]
		
		\item \textbf{Jihoon Lee}, Seungyun Jung, Seong-hun Kim, Hanna Lee, and Youdan Kim, "Flight Control of Asymmetric Variable-Span Morphing Aircraft Using Nonlinear Dynamic Inversion," \textit{11th Asia-Pacific International Symposium on Aerospace Technology (APISAT 2019)}, Gold Coast, Australia, Dec. 2019. 
	
		\item Seong-hun Kim, \textbf{Jihoon Lee}, Seungyun Jung, Hanna Lee, and Youdan Kim, "Deep Neural Network-Based Feedback Control for Dynamic Soaring," \textit{21st IFAC Symposium on Automatic Control in Aerospace (ACA 2019)}, Cranfield, UK, Aug. 2019. \newline[DOI: 10.1016/j.ifacol.2019.11.079]
		
		\item Hanna Lee, \textbf{Jihoon Lee}, Seong-hun Kim, Seungyun Jung, and Youdan Kim, "Adaptive Control Allocation-based Control Design for Non-affine Morphing Aircraft System," \textit{9th European Conference for Aeronautics and Space Sciences (EUCASS 2019)}, Madrid, Spain, Jul. 2019. \newline[DOI: 10.13009/EUCASS2019-163]
		
		\item \textbf{Jihoon Lee}, Seong-hun Kim, Seungyun Jung, Hanna Lee, and Youdan Kim, "Linear Parameter-Varying Control of Variable Span-Sweep Morphing Aircraft," \textit{Guidance, Navigation, and Control Conference, AIAA Science and Technology Forum and Exposition (SciTech 2019)}, San Diego, CA, USA, Jan. 2019. \newline[DOI: 10.2514/6.2019-0106]
		
		\item Hanna Lee, \textbf{Jihoon Lee}, Seong-hun Kim, Seungyun Jung, and Youdan Kim, "Control Design for Morphing Aircraft Based on Frequency-Apportioned Control Allocation," \textit{10th Asia-Pacific International Symposium on Aerospace Technology (APISAT 2018)}, Chengdu, China, Oct. 2018. 
		
		\item \textbf{Jihoon Lee}, and Youdan Kim, "Quasi-LPV Modeling and Parameter-dependent Optimal Control of Morphing Wing Aircraft," \textit{31st Congress of the International Council of the Aeronautical Sciences (ICAS 2018)}, Belo Horizonte, Brazil, Sep. 2018. 
		
		\item \textbf{Jihoon Lee}, Seong-hun Kim, Seungyun Jung, Hanna Lee, and Youdan Kim, "Sliding Mode Control Design for a Multidimensional Morphing UAV," \textit{6th European Control Conference (ECC 2018)}, Limassol, Cyprus, Jun. 2018. \newline[DOI: 10.23919/ECC.2018.8550259]
		
		\item \textbf{Jihoon Lee}, and Youdan Kim, "Neural Network-Based Nonlinear Dynamic Inversion Control of Variable-Span Morphing Aircraft," \textit{8th European Conference for Aeronautics and Space Sciences (EUCASS 2017)}, Milan, Italy, Jul. 2017. \newline[DOI: 10.13009/EUCASS2017-195]
		
		\item \textbf{Jihoon Lee}, Seokwon Lee, Somang Lee, Youdan Kim, Jungha Park, Seungkeun Kim, and Jinyoung Suk, "Stochastic Approach to Risk Evaluation for UAV Landing on an Aircraft Carrier," \textit{7th Asia-Pacific International Symposium on Aerospace Technology (APISAT 2015)}, Cairns, Australia, Nov. 2015. 
		
		\item Somang Lee, \textbf{Jihoon Lee}, Seokwon Lee, Youdan Kim, Jinyoung Suk, and Seungkeun Kim, "A Study on Autonomous UAV Take-off and Landing on a Carrier," \textit{7th Asia-Pacific International Symposium on Aerospace Technology (APISAT 2015)}, Cairns, Australia, Nov. 2015. 
	\end{enumerate}\renewcommand{\labelenumi}{\theenumi.}
	
	\textbf{NATIONAL JOURNAL}
	\begin{enumerate}\renewcommand{\labelenumi}{[NJ.\theenumi]}
		\item Heein Park, \textbf{Jihoon Lee}, Youdan Kim, Jae Hong Lee, and Chan Gook Park, "Development of an Indoor Path Planning System for Search and Rescue Operations of the Firefighters," \textit{Journal of Positioning, Navigation, and Timing}, In Preparation.
	\end{enumerate}\renewcommand{\labelenumi}{\theenumi.}
	
	\textbf{NATIONAL CONFERENCE}
	\begin{enumerate}\renewcommand{\labelenumi}{[NC.\theenumi]}
		\item \textbf{Jihoon Lee}, Hyeonggwan Kang, Sangmin Lee, Youdan Kim, Jinyoung Suk, Seungkeun Kim, "Control Surface Modeling and Control Authority Analysis for Longitudinal Motion of Control-Configured Vehicle," \textit{2021 KSAS Fall Conference (KSAS 2021F)}, Jeju, Korea, Nov. 2021.
		
		\item Heein Park, \textbf{Jihoon Lee}, Youdan Kim, Chan Gook Park, and Jae Hong Lee, "Development of an Indoor Path Planning System for Search and Rescue Operations of the Firefighters," \textit{2021 IPNT Conference (IPNT 2021)}, Gangneung, Korea, Nov. 2021. 
		
		\item \textbf{Jihoon Lee}, Suwon Lee, Youngjun Lee, Youdan Kim, Young-jun Heo, and Tae-dong Yoon, "Maneuvering Target Tracking with Anomalous Measurement Errors of Laser Range Finder," \textit{2020 KSAS Fall Conference (KSAS 2020F)}, Jeju, Korea, Nov. 2020. 
		
		\item \textbf{Jihoon Lee}, Seungyun Jung, Seong-hun Kim, Hanna Lee, and Youdan Kim, "Modeling and Simulation of Asymmetric Variable-Span Morphing Aircraft," \textit{2019 KSAS Fall Conference (KSAS 2019F)}, Jeju, Korea, Nov. 2019. 
		
		\item Hanna Lee, Seong-hun Kim, \textbf{Jihoon Lee}, Seungyun Jung, and Youdan Kim, "Partially Model-Free Control Design for Morphing Aircraft using Adaptive Dynamic Programming," \textit{2019 KSAS Fall Conference (KSAS 2019F)}, Jeju, Korea, Nov. 2019. 
		
		\item Hanna Lee, Seong-hun Kim, \textbf{Jihoon Lee}, and Youdan Kim, "Morphing Aircraft Inverse Dynamics Learning and Control Based on Gaussian Processes," \textit{2019 KSAS Spring Conference (KSAS 2019S)}, Buan, Korea, Apr. 2019. 
		
		\item \textbf{Jihoon Lee}, Seong-hun Kim, Seungyun Jung, Hanna Lee, and Youdan Kim, "Performance Map of Morphing Aircraft for Hierarchical Control," \textit{2018 KSAS Fall Conference (KSAS 2018F)}, Jeju, Korea, Nov. 2018. 
		
		\item Hanna Lee, \textbf{Jihoon Lee}, Yongjun Seo, and Youdan Kim, "Robust Closed-loop Control Allocation for Morphing Aircraft," \textit{2018 KSAS Fall Conference (KSAS 2018F)}, Jeju, Korea, Nov. 2018. 
		
		\item \textbf{Jihoon Lee}, Seungyun Jung, S, Kim, Hanna Lee, Youdan Kim, and Jaesung Bae, "Hierarchical Flight Control System for Morphing Aircraft," \textit{2018 SASE Fall Conference (SASE 2018F)}, Gyeongju, Korea, Nov. 2018. 
		
		\item Hanna Lee, \textbf{Jihoon Lee}, Seong-hun Kim, Seungyun Jung, and Youdan Kim, "Control Design of Variable Span-Sweep Morphing wing UAV Using control Allocation," \textit{2018 KSAS Spring Conference (KSAS 2018S)}, Goseong, Korea, Apr. 2018. 
		
		\item \textbf{Jihoon Lee}, Seungyun Jung, Seong-hun Kim, Hanna Lee, and Youdan Kim, "Quasi-Linear Parameter-Varying Modeling of Variable-Span Morphing Aircraft Longitudinal Motion," \textit{2017 KSAS Fall Conference (KSAS 2017F)}, Jeju, Korea, Nov. 2017. 
		
		\item Seong-hun Kim, \textbf{Jihoon Lee}, Seungyun Jung, and Youdan Kim, "Spectral Analysis of Model Reference Adaptive Control System," \textit{2017 KSAS Fall Conference (KSAS 2017F)}, Jeju, Korea, Nov. 2017. 
		
		\item Byunghoon Kim, Suwon Lee, Jaeho Lee, Somang Lee, \textbf{Jihoon Lee}, Namhoon Cho, Youdan Kim, and Gwanghyeok Ju, "Conceptual Study of an AOCS Simulator and Three Dimensional Visualization Environment for Lunar Orbiter," \textit{2017 KSAS Spring Conference (KSAS 2017S)}, Samcheok, Korea, Apr. 2017. 
		
		\item \textbf{Jihoon Lee}, Seong-hun Kim, Seungyun Jung, Jaesung Bae, Seungkeun Kim, and Youdan Kim, "Flight Control of a Variable Span Morphing Wing UAV," \textit{2017 KSAS Spring Conference (KSAS 2017S)}, Samcheok, Korea, Apr. 2017. 
		
		\item Seungyun Jung, Seong-hun Kim, \textbf{Jihoon Lee}, Jaesung Bae, Seungkeun Kim, and Youdan Kim, "Flight Control of a Variable Span Morphing Aircraft during Transition Phase," \textit{2017 KSAS Spring Conference (KSAS 2017S)}, Samcheok, Korea, Apr. 2017. 
		
		\item Suwon Lee, \textbf{Jihoon Lee}, Byunghoon Kim, Youdan Kim, and Gwanghyeok Ju, "Grid Modeling of Solar Radiation Pressure and Effect on Earth-Lunar Transfer Trajectory," \textit{2017 KSAS Spring Conference (KSAS 2017S)}, Samcheok, Korea, Apr. 2017. 
		
		\item \textbf{Jihoon Lee}, Suwon Lee, Byunghoon Kim, Youdan Kim, and Gwanghyeok Ju, "Spacecraft Attitude Maneuver Control Using Linear Model Following Nonlinear Adaptive Controller," \textit{2016 KSAS Spring Conference (KSAS 2016S)}, Goseong, Korea, Apr. 2016. 
		
		\item Byunghoon Kim, Namhoon Cho, Jaeho Lee, Somang Lee, \textbf{Jihoon Lee}, Suwon Lee, Youdan Kim, and Gwanghyeok Ju, "A Primary Study on the Control System for Lunar Orbiter Using Autocode Generation," \textit{2016 KSAS Spring Conference (KSAS 2016S)}, Goseong, Korea, Apr. 2016. 
		
		\item \textbf{Jihoon Lee}, Seokwon Lee, Somang Lee, Donghae Kim, and Youdan Kim, "Risk Evaluation Scheme in Automatic Aircraft Carrier Landing Using Artificial Neural Network," \textit{3rd Aviation-Specialized University Conference}, Seoul, Korea, Feb. 2016.
		
		\item \textbf{Jihoon Lee}, Seokwon Lee, Jungha Park, Youdan Kim, Seong-hun Kim, and Jinyoung Suk, "A Decision Making Technique for UAV Automatic Carrier Landing System," \textit{2015 KSAS Spring Conference (KSAS 2015S)}, Jeongseon, Korea, Apr. 2015. 
	\end{enumerate}\renewcommand{\labelenumi}{\theenumi.}
\end{rSection}


\begin{rSection}{Projects}

{\bf Development of Ground Control and Communication System for VTOL Fixed-Wing Drone} \hfill {\em May 2021 - Present} 
\\{\textit{ Agency for Defense Development}}
\\{\textit{ Research Assistant}}
%\\- xxx
%\\- xxx

{\bf Development of Location System for Firefighters Based on Wireless Communication} \hfill {\em Jan 2021 - Present} 
\\{\textit{ Korea Fire Institute}}
\\{\textit{ Research Assistant}}
%\\- xxx
%\\- xxx

{\bf Development of Target Tracking Algorithms} \hfill {\em Jan 2020 - Aug 2020} 
\\{\textit{ LIG Nex1 Company Ltd.}}
\\{\textit{ Research Assistant}}
%\\- xxx
%\\- xxx

{\bf Development of an SMPC Flap Module for Morphing Wings} \hfill {\em Jun 2016 - Dec 2020} 
\\{\textit{ Ministry of Trade, Industry and Energy}}
\\{\textit{ Research Assistant}}
%\\- xxx
%\\- xxx

{\bf Development of Guidance, Navigation, and Control Algorithms and Corresponding Source Code for Experimental Lunar Orbiter} \hfill {\em Sep 2014 - Jun 2017} 
\\{\textit{ Ministry of Science, ICT and Future Planning}}
\\{\textit{ Research Assistant}}
%\\- xxx
%\\- xxx

{\bf Guidance/Control Study for Take-off and Landing on a Ship} \hfill {\em Nov 2014 - Dec 2015} 
\\{\textit{ Agency for Defense Development}}
\\{\textit{ Research Assistant}}
%\\- xxx
%\\- xxx



\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%\begin{rSection}{Work Experience}
%
%
%{\bf Work Station x,Strange Place x} \hfill {\em June 20xx - April 20xx} 
%\\{\textit{ Engineer}}
%\\- xxx
%\\- xxx
%
%{\bf Work Station x,Strange Place x} \hfill {\em June 20xx - April 20xx} 
%\\{\textit{ Engineer}}
%\\- xxx
%\\- xxx
%
% \\- xx
% \\- xx
% 
%
%
%
%\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%\begin{rSection}{Experience}
%
%
%{\bf Space Development: Theory and Practice} \hfill {\em June 20xx - April 20xx} 
%\\{\textit{ Youth Space Center, Bauman Moscow State Technical University}}
%
%{\bf Short Course} \hfill {\em June 20xx - April 20xx} 
%\\{\textit{ Chungnam National University}}




%\end{rSection}

%----------------------------------------------------------------------------------------
%	Extracurricular Section

%----------------------------------------------------------------------------------------
%\begin{rSection}{Extracurricular }
%
%
%{\bf Lifeguard Certification} \hfill {\em June 20xx - April 20xx} 
%\\{\textit{ Korean Red Cross}}
%
%{\bf Driver's License} \hfill {\em June 20xx - April 20xx} 
%\\{\textit{ Title}}
%
%
%
%\end{rSection}
\begin{rSection}{Award}
{\bf Grand Prize (Transport Minister's Award)} \hfill {\em Jan 2015} \\ 
\textit{3rd Aviation-Specialized University Conference, Mayfield Hotel, Seoul, Republic of Korea} \\

\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------



% \newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------

\end{document}